The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-08-31 ms/ms.tex
overleaf

Uncertainty in the model projections of the carbon cycle is manifest in both uncertainty around the appropriate algorithms and model structures used, and also in the parameterizations of these models (Luo and Schuur 2020). Model inter-comparison projects (MIPs) are the primary means by which structural uncertainty is assessed (refs). While these have had tremendous utility in capturing and assessing wide ranges of model assumptions, it can nonetheless be difficult to interpret the differences between models, or even between subsequent versions of the same model, due to the multiplicity of structural and parametric variations \cite{mcneall2016}. To allow for more tractable experimental design each model is typically allowed only a single parameterization (despite the existence of many plausible parameter sets) due to the cost of conducting multiple experiments with different parameterizations (e.g., in the case of the TRENDY land model intercomparison or CMIP). Thus, MIPs typically conflate parametric and structural uncertainty, and de-emphasize the consequences of uncertain model calibration in estimates of future land state trajectories.

@@

Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large parameter perturbation ensembles (PPEs) \cite{qian2018}. 
PPEs have played an important role in assessing projection uncertainty in climate models \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013,williamson2017,hourdin2020,couvreux2021} or Bayesian uncertainty quantification \cite{cleary2021}. A parameter sensitivity analysis was conducted with ORCHIDEE using a semi-analytic spin-up (SASU) offered by a matrix approach to understand 34 biogeochemistry parameters according to variance explained by each parameter (Huang et al. 2018). 
A major goal of this project is to enable automated calibration of the Community Land Model (CLM) \cite{lawrence2019}. This extends the work of \citeA{dagon2020} which utilized a PPE to calibrate a subset of CLM parameters. Here we include a broader suite of parameters and continue to enhance the software tools for parameter perturbation and optimization.

>>>>

Uncertainty in the model projections of the carbon cycle is manifest in uncertainty around the appropriate algorithms and equations used, and also in the parameterizations of these models \cite{luo2020}. Model inter-comparison projects (MIPs) are the primary means by which structural uncertainty is assessed. While these have had tremendous utility in capturing and assessing wide ranges of model assumptions, it can nonetheless be difficult to interpret the differences between models, or even between subsequent versions of the same model, due to the multiplicity of structural and parametric variations \cite{mcneall2016}. To allow for more tractable experimental design each model is typically allowed only a single parameterization (despite the existence of many plausible parameter sets) due to the cost of conducting multiple experiments with different parameterizations (e.g., in the case of the TRENDY land model intercomparison or CMIP). Thus, MIPs typically conflate parametric and structural uncertainty, and de-emphasize the consequences of uncertain model calibration in estimates of future land state trajectories.

@@

Several promising avenues for model calibration are in development \cite{pinnington2020,cleary2021,alonso-gonzalez2022}, many of which require the construction of large parameter perturbation ensembles (PPEs) \cite{qian2018}. 
PPEs have played an important role in assessing projection uncertainty in climate models \cite{murphy2004,sanderson2008,booth2012,hawkins2019,yamazaki2021,peatier2022,tett2022}.
PPEs also form a basis for automated model calibration through, for example, history matching \cite{williamson2013,williamson2017,hourdin2020,couvreux2021} or Bayesian uncertainty quantification \cite{cleary2021}. A parameter sensitivity analysis was conducted with the Organizing Carbon and Hydrology in Dynamic Ecosystems (ORCHIDEE) using a semi-analytic spin-up (SASU) offered by a matrix approach to understand 34 biogeochemistry parameters according to variance explained by each parameter (Huang et al. 2018). 
A major goal of this project is to enable automated calibration of the Community Land Model (CLM) \cite{lawrence2019}. This extends the work of \citeA{dagon2020} which utilized a PPE to calibrate a subset of CLM parameters. Here we include a broader suite of parameters and continue to enhance the software tools for parameter perturbation and optimization.
